### 2018-08-15 memocode_cr/related.tex
Add MEMOCODE'17 camera ready and presentation files

Theorem proving with SMT solvers is not a new idea. S. Merz and H. Vanzetto~\cite{Merz2012TLASMT} has proposed a backend using SMT solvers to assist discharging proof obligations of TLA{\thinspace}+{\thinspace}. D. Kr\"oning et al.~\cite{smtLSM2009} has proposed a theory of finit sets, lists, and maps for SMT-LIB. The proposed theory is general but limited in basic types of {\tt Int} and {\tt Real}. The authors only discussed how to realize the theory by reduction to existing SMT theories with a report of initial benchmarks\footnote{http://www.cprover.org/SMT-LIB-LSM/} on a Event-B case study. The idea of adopting existing theories of SMT is the same as our approach. However, we argue that a strategic encoding like our approach might is necessary for discharging VDM POs than introducing general theories because the infinite and undecidable nature of sets, lists, and maps in VDM.

>>>>

Theorem proving with SMT solvers is not a new idea. S. Merz and H. Vanzetto~\cite{Merz2012TLASMT} has proposed a backend using SMT solvers to assist discharging proof obligations of TLA{\thinspace}+{\thinspace}. D. Kr\"oning et al.~\cite{smtLSM2009} has proposed a theory of finit sets, lists, and maps for SMT-LIB. The proposed theory is general but limited in basic types of {\tt Int} and {\tt Real}. The authors only discussed how to realize the theory by reduction to existing SMT theories with a report of initial benchmarks\footnote{http://www.cprover.org/SMT-LIB-LSM/} on a Event-B case study. The idea of adopting existing theories of SMT is the same as our approach. However, we argue that a strategic encoding like our approach is necessary for discharging VDM POs than introducing general theories because the infinite and undecidable nature of sets, lists, and maps in VDM.
